Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-03 Draft/draft.tex
Added a few comments

Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$, then a perfect strategy for 
the linear system game ($H\ux = \uc$) is given by 
\begin{enumerate}
	\item $M_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $N_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
	\hf{I don't think we need to take transpose because these are binary observables. -HF}
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
\hf{Later we will use this approach to construct a strategy for a linear system game.}
\carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}
\hfc{How about now?}
However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.

@@

%------------------------------------------------------------------------
\subsection{The embedding of $uou^{-1} = o^r$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma_r$ of the linear system game,
so we denote the linear system game by $\LS(\Gamma_r)$.
\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$? Or you have any suggestion about a symbol for this group?}
We also prove some properties of the generators of $\Gamma_r$ along the way.

>>>>

Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$, then a perfect strategy for 
the linear system game ($H\ux = \uc$) is given by 
\begin{enumerate}
	\item $M_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $N_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
	\hf{I don't think we need to take transpose because these are binary observables. -HF}  \carl{A binary observable can still be different from its transpose.}
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.

@@

%------------------------------------------------------------------------
\subsection{The embedding of $uou^{-1} = o^r$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma_r$ of the linear system game,
so we denote the linear system game by $\LS(\Gamma_r)$.
\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$? Or you have any suggestion about a symbol for this group?} \carl{The notation that you're using seems backwards -- I think we should express the solution group as a function of the linear system, not the other way around.}
We also prove some properties of the generators of $\Gamma_r$ along the way.
